---
author: "Killian, Luca, Aranxa"
title: "Quanteda"
subtitle: "Analysing text data quantitively"
output: 
  html_document:
    toc: TRUE
    df_print: paged
    number_sections: FALSE
    highlight: tango
    theme: lumen
    toc_depth: 3
    toc_float: true
    css: custom.css 
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Insert session Intro here

---
# Loading the package
If 

First we load the core of the quantedata package. If any of the packages are not installed on your machine you can uncomment the first line.

```{r initialise, warning=FALSE}
#install.packages('quanteda','quanteda.textstats','readtext')

library(quanteda)
```

```{r initialise2, warning=FALSE}
library(quanteda.textstats)
```

The package is split in to modular packages so we also download a selection of those of interest to us in this tutorial.

Finally we load readtext which makes the process of importing texts easier, and also imports meta data. Specifically in our case, it allows us to read in pdfs as text files.

```{r initialise3, warning=FALSE}
library(readtext)
```

#Loading and prepping our data - The Corpus

For the example in this tutorial we will load in a collection of slides from the Intro to Data Science Course by Simon Munzert. We use the readtext function as mentioned above.

```{r}
rt_pdf <- readtext("./Slideshows/*.pdf", docvarsfrom = "filenames")
#rt_pdf <- readtext("./Slideshows/*.pdf", docvarsfrom = "filenames", dvsep = "-")
```

We encourage you to add your own slideshow in pdf format. To do this, just insert the pdf file in the Input folder. For demonstration purposes we have included the slideshow you just saw, but we think that this demonstration will be more interesting and fun if you can add your own data.

```{r}
rt_pdf <- readtext("./Slideshows/*.pdf", docvarsfrom = "filenames")

```


```{r}

```



```{r}
slideshow_corpus = corpus(rt_pdf)
summary(slideshow_corpus)

slideshow_tokens = tokens(slideshow_corpus, remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE)
```



```{r}
slideshow_tokens = tokens_remove(slideshow_tokens, stopwords("en"))

slideshow_dfm = dfm(slideshow_tokens)

textstat_lexdiv(slideshow_dfm)

topfeatures(slideshow_dfm)

#idea: find most similar slideshows, 'whihc IDS lecture is yours?'
```
